---
title: "ruishan"
author: "Ruishan Han"
output:  
  flexdashboard::flex_dashboard:
    storyboard: true
---

### Background

As an Asian student, I have a strong appreciation for Chinese and Japanese music. 
However, I lack a formal music background, which makes it challenging for me to create my own compositions. 
To overcome this, I turned to artificial intelligence for assistance by using Stable Audio as the AI tool to generate music. 


First, I input prompts including Drum Kit, Flowing, Raw, Epic, Chinese Traditional Music, and Sentimental. 
The outcome is this piece: https://stableaudio.com/1/share/60e8141d-6ac9-4928-8bf2-0d6d6e420736.

This is the audio of the AI generated Chinese music track:

<div>
  <audio controls>
    <source src="ruishan-h-1.mp3" type="audio/mpeg">
    Your browser does not support the audio element.
  </audio>
</div>


Furthermore, I use prompts that included Drum Kit, Flowing, Raw, Epic, Japanese Traditional Music, and Sentimental, 
which resulted in this track: https://stableaudio.com/1/share/c8d896b9-e6ba-4646-a3bc-c81682f47011.

This is the audio of the AI generated Japanese music track:

<div>
  <audio controls>
    <source src="ruishan-h-2.mp3" type="audio/mpeg">
    Your browser does not support the audio element.
  </audio>
</div>







### Track-level features

```{r}




```









### Chroma features [pitch]



```{r}

library(tidyverse)
source("compmus.R")

"features/ruishan-h-1.json" |>                           # Change the track
  compmus_chroma(norm = "identity") |>                 # Change the norm
  ggplot(aes(x = time, y = pc, fill = value)) + 
  geom_raster() +
  scale_y_continuous(
    breaks = 0:11,
    minor_breaks = NULL,
    labels = c(
                "C", "C#|Db", "D", "D#|Eb",
                "E", "F", "F#|Gb", "G",
                "G#|Ab", "A", "A#|Bb", "B"
              )
  ) +
  scale_fill_viridis_c(guide = "none") +               # Change the colours?
  labs(x = "Time (s)", y = NULL, fill = NULL) +
  theme_classic()                                      # Change the theme?






```







`







```


hello

### Loudness [volume]


```{r}




"features/ruishan-h-2.json" |>                           # Change the track
  compmus_chroma(norm = "identity") |>                 # Change the norm
  ggplot(aes(x = time, y = pc, fill = value)) + 
  geom_raster() +
  scale_y_continuous(
    breaks = 0:11,
    minor_breaks = NULL,
    labels = c(
                "C", "C#|Db", "D", "D#|Eb",
                "E", "F", "F#|Gb", "G",
                "G#|Ab", "A", "A#|Bb", "B"
              )
  ) +
  scale_fill_viridis_c(guide = "none") +               # Change the colours?
  labs(x = "Time (s)", y = NULL, fill = NULL) +
  theme_classic()                                      # Change the theme?


















```









### Timbre features [timbre]

```{r}
#      C     C#    D     Eb    E     F     F#    G     Ab    A     Bb    B
major_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    0,    0)
minor_chord <-
  c(   1,    0,    0,    1,    0,    0,    0,    1,    0,    0,    0,    0)
seventh_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    1,    0)

major_key <-
  c(6.35, 2.23, 3.48, 2.33, 4.38, 4.09, 2.52, 5.19, 2.39, 3.66, 2.29, 2.88)
minor_key <-
  c(6.33, 2.68, 3.52, 5.38, 2.60, 3.53, 2.54, 4.75, 3.98, 2.69, 3.34, 3.17)

chord_templates <-
  tribble(
    ~name, ~template,
    "Gb:7", circshift(seventh_chord, 6),
    "Gb:maj", circshift(major_chord, 6),
    "Bb:min", circshift(minor_chord, 10),
    "Db:maj", circshift(major_chord, 1),
    "F:min", circshift(minor_chord, 5),
    "Ab:7", circshift(seventh_chord, 8),
    "Ab:maj", circshift(major_chord, 8),
    "C:min", circshift(minor_chord, 0),
    "Eb:7", circshift(seventh_chord, 3),
    "Eb:maj", circshift(major_chord, 3),
    "G:min", circshift(minor_chord, 7),
    "Bb:7", circshift(seventh_chord, 10),
    "Bb:maj", circshift(major_chord, 10),
    "D:min", circshift(minor_chord, 2),
    "F:7", circshift(seventh_chord, 5),
    "F:maj", circshift(major_chord, 5),
    "A:min", circshift(minor_chord, 9),
    "C:7", circshift(seventh_chord, 0),
    "C:maj", circshift(major_chord, 0),
    "E:min", circshift(minor_chord, 4),
    "G:7", circshift(seventh_chord, 7),
    "G:maj", circshift(major_chord, 7),
    "B:min", circshift(minor_chord, 11),
    "D:7", circshift(seventh_chord, 2),
    "D:maj", circshift(major_chord, 2),
    "F#:min", circshift(minor_chord, 6),
    "A:7", circshift(seventh_chord, 9),
    "A:maj", circshift(major_chord, 9),
    "C#:min", circshift(minor_chord, 1),
    "E:7", circshift(seventh_chord, 4),
    "E:maj", circshift(major_chord, 4),
    "G#:min", circshift(minor_chord, 8),
    "B:7", circshift(seventh_chord, 11),
    "B:maj", circshift(major_chord, 11),
    "D#:min", circshift(minor_chord, 3)
  )

key_templates <-
  tribble(
    ~name, ~template,
    "Gb:maj", circshift(major_key, 6),
    "Bb:min", circshift(minor_key, 10),
    "Db:maj", circshift(major_key, 1),
    "F:min", circshift(minor_key, 5),
    "Ab:maj", circshift(major_key, 8),
    "C:min", circshift(minor_key, 0),
    "Eb:maj", circshift(major_key, 3),
    "G:min", circshift(minor_key, 7),
    "Bb:maj", circshift(major_key, 10),
    "D:min", circshift(minor_key, 2),
    "F:maj", circshift(major_key, 5),
    "A:min", circshift(minor_key, 9),
    "C:maj", circshift(major_key, 0),
    "E:min", circshift(minor_key, 4),
    "G:maj", circshift(major_key, 7),
    "B:min", circshift(minor_key, 11),
    "D:maj", circshift(major_key, 2),
    "F#:min", circshift(minor_key, 6),
    "A:maj", circshift(major_key, 9),
    "C#:min", circshift(minor_key, 1),
    "E:maj", circshift(major_key, 4),
    "G#:min", circshift(minor_key, 8),
    "B:maj", circshift(major_key, 11),
    "D#:min", circshift(minor_key, 3)
  )
library(tidyverse)
source("compmus.R")

"features/ruishan-h-1.json" |> 
  compmus_chroma(norm = "identity") |> 
  compmus_match_pitch_templates(
    key_templates,         # Change to chord_templates if desired
    norm = "identity",       # Try different norms (and match it with what you used in `compmus_chroma`)
    distance = "cosine"   # Try different distance metrics
  ) |>
  ggplot(aes(x = time, y = name, fill = d)) + 
  geom_raster() +
  scale_fill_viridis_c(guide = "none") +               # Change the colours?
  labs(x = "Time (s)", y = "Template", fill = NULL) +
  ggtitle("The Chordogram of AI generated Chinese music track") +  
  theme_classic()                                      # Change the theme?



library(tidyverse)
source("compmus.R")

source("compmus.R")

"features/ruishan-h-2.json" |> 
  compmus_chroma(norm = "identity") |> 
  compmus_match_pitch_templates(
    key_templates,         # Change to chord_templates if desired
    norm = "identity",       # Try different norms (and match it with what you used in `compmus_chroma`)
    distance = "cosine"   # Try different distance metrics
  ) |>
  ggplot(aes(x = time, y = name, fill = d)) + 
  geom_raster() +
  scale_fill_viridis_c(guide = "none") +               # Change the colours?
  labs(x = "Time (s)", y = "Template", fill = NULL) +
  ggtitle("The Chordogram of AI generated Japanese music track") +  
  theme_classic()                                      # Change the theme?











```













### Temporal features [duration]





### Clustering




### Contribution